---
title: "Get continuum limit Lagrangian Matching"
author: "Christiane"
date: "2024-11-22"
output:
  pdf_document: default
  html_document: default
---

```{r setup}
knitr::opts_chunk$set(echo = FALSE)
library("hadron")
source("~/Documents/masterthesis/analyse_potential/myfunctions.R")
source("~/Documents/masterthesis/analyse_potential/matchwithellipse.R")

hamiltoniandata <- read.table("/home/gross/Documents/masterthesis/more_measurements/hamiltonian/interpolate_ham.csv", header = T)
lagrangiandatacollection <- readRDS("/home/gross/Documents/masterthesis/more_measurements/heatbath/contlim/plotstikz/ellipseparameters.RData")

ldata <- lagrangiandatacollection$data

resellipsemean <- lagrangiandatacollection$resellipsemean
listellipsemean <- split(cbind(resellipsemean, ldata), f = seq(nrow(resellipsemean)))

resellipsemedian <- lagrangiandatacollection$resellipsemedian
listellipsemedian <- split(cbind(resellipsemedian, ldata), f = seq(nrow(resellipsemedian)))

resellipsemeanratio <- lagrangiandatacollection$resellipseratio
listellipsemeanratio <- split(cbind(resellipsemeanratio, ldata), f = seq(nrow(resellipsemean)))

resellipsemedianratio <- lagrangiandatacollection$resellipseratiomedian
listellipsemedianratio <- split(cbind(resellipsemedianratio, ldata), f = seq(nrow(resellipsemedian)))

names(listellipsemedian[[1]])


```

Because the ellipse is two-dimensional and not one-dimensiona, we have to convert the radius enlargement that is needed for matching to a confidence level.

$s=-2*log(1-p)$. $p$ of all points are in an ellipse with the "radius" $\sqrt{s}$, which we have identified as devstd from the matching ellipse.

$\text{devstd}^2=2*log(1-p) \Leftrightarrow p = 1-\exp(-0.5*\text{devstd}^2)$

$p=pnorm(n)-pnorm(-n)$

$0=pnorm(n)-pnorm(-n) - (1-\exp(-0.5*\text{devstd}^2))$

From the probability we can find the confidence level/level of deviation with root-finding.


```{r summarydirect}
fninterval <- function(x, devstd) (pnorm(x)-pnorm(-x) - (1-exp(-0.5*devstd^2)))
summarisedata <- function(ldata, errtype, xiinter, listellipse=listellipsemean, meanormedian="mean", resellipse=resellipsemean, plotellipse=T, ...) {
  stopifnot(meanormedian=="mean" || meanormedian=="median")
  if(meanormedian=="mean") {
    errbeta <- "dbetacontlim"
    errplaq16 <- "dplaq16contlim"
    errplaq3 <- "dplaq3contlim"
    longres <- data.frame(beta=c(), mode=c(), betamatch=c(), dev=c(), rad=c(), 
                          betamatchstat=c(), betamatchsys=c(), betamatchspread=c(), 
                          P3=c(), P3stat=c(), P3sys=c(), P3spread=c(), 
                          P16=c(), P16stat=c(), P16sys=c(), P16spread=c())
  } else {
    errbeta <- "q84beta"
    errplaq16 <- "q84plaq16"
    errplaq3 <- "q84plaq3"
    longres <- data.frame(beta=c(), mode=c(), betamatch=c(), dev=c(), rad=c(), 
                          betamatchstatq16=c(), betamatchsysq16=c(), betamatchspreadq16=c(), betamatchstatq84=c(), betamatchsysq84=c(), betamatchspreadq84=c(), 
                          P3=c(), P3statq16=c(), P3sysq16=c(), P3spreadq16=c(), P3statq84=c(), P3sysq84=c(), P3spreadq84=c(), 
                          P16=c(), P16statq16=c(), P16sysq16=c(), P16spreadq16=c(), P16statq84=c(), P16sysq84=c(), P16spreadq84=c())
  }
  mask <- ldata$errtype==errtype & ldata$xiinter==xiinter
  maskresellipse <- resellipse$errtype==errtype & resellipse$xiinter==xiinter
  
  plot(NA, xlab="beta", ylab="P", ylim=c(0.60, 0.67), xlim=c(1.35, 1.49), ...)
  modes <- c("xi0.18", "xi0.19", "xi0.20", "xi0.18wo0.19")
  cols <- c("red", "blue", "darkgreen", "magenta")
  pchs <- c(21, 22, 23)
  shortres <- data.frame(betamatch1.65=c(), dev1.65=c(), rad1.65=c(), betamatch1.7=c(), dev1.7=c(), rad1.7=c())
  
  for(index in seq_along(modes)) {
    mode=modes[index]
    # print(ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ])
    dx <- array(NA, dim=c(2, 3))
    dx[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errbeta]
    dx[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ][, errbeta]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errbeta]^2)
    dx[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ][, errbeta]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errbeta]^2)
    dy <- array(NA, dim=c(2, 3))
    dy[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq3]
    dy[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ][, errplaq3]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq3]^2)
    dy[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ][, errplaq3]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq3]^2)
    if(meanormedian=="mean") {
      plotwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$betacontlim, 
                    y=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$plaq3contlim, 
                    dx=dx, dy=dy, errsum.method = "quadrature", rep=T, col=cols[index], bg=cols[index], pch=pchs[index], ...)
      if(plotellipse) {
        plotlims <- lapply(listellipse[which(resellipse$errtype==errtype & resellipse$xiinter==xiinter & resellipse$mode==mode & resellipse$etp==1 & resellipse$spread==T)], 
                           FUN = function(x) draw_ellipse_general(meanx = x$betacontlim, meany = x$plaq3contlim, 
                                                                  radx = x$dbetacontlim, rady = x$dplaq3contlim, 
                                                                  phi = x$theta, nstd = x$devstd, 
                                                                  rep = T, cex = 0.01, points = 5000, col=cols[index]))
      }
      
      newline <- data.frame(beta=c(1.65, 1.7), mode=mode, betamatch=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$betacontlim, dev=NA, rad=NA, 
                            betamatchstat=dx[, 1], betamatchsys=dx[, 2], betamatchspread=dx[, 3],
                            P3=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$plaq3contlim, 
                            P3stat=dy[, 1], P3sys=dy[, 2], P3spread=dy[, 3])
    } else {
      mdx <- array(NA, dim=c(2, 3))
      mdx[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta 
      mdx[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ]$q16beta^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta^2)
      mdx[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$q16beta^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta^2)
      mdy <- array(NA, dim=c(2, 3))
      mdy[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq3 
      mdy[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ]$q16plaq3^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq3^2)
      mdy[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$q16plaq3^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq3^2)
      plotwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianbeta, 
                    y=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianplaq3, 
                    dx=dx, dy=dy, mdy=mdy, mdx=mdx, errsum.method = "quadrature", rep=T, col=cols[index], bg=cols[index], pch=pchs[index], ...)
      if(plotellipse) {
        plotlims <- lapply(listellipse[which(resellipse$errtype==errtype & resellipse$xiinter==xiinter & resellipse$mode==mode & resellipse$etp==1 & resellipse$spread==T)], 
                           FUN = function(x) draw_ellipse_general(meanx = x$medianbeta, meany = x$medianplaq3, 
                                                                  radx = x$q16beta, rady = x$q84plaq3, 
                                                                  phi = x$theta, nstd = as.numeric(x$devstd), 
                                                                  rep = T, cex = 0.01, points = 5000, col=cols[index]))
      }
      
      newline <- data.frame(beta=c(1.65, 1.7), mode=mode, betamatch=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianbeta, dev=NA, rad=NA, 
                            betamatchstatq16=dx[, 1], betamatchsysq16=dx[, 2], betamatchspreadq16=dx[, 3], betamatchstatq84=mdx[, 1], betamatchsysq84=mdx[, 2], betamatchspreadq84=mdx[, 3],
                            P3=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianplaq3, 
                            P3statq16=dy[, 1], P3sysq16=dy[, 2], P3spreadq16=dy[, 3], P3statq84=mdy[, 1], P3sysq84=mdy[, 2], P3spreadq84=mdy[, 3])
    }
    
    
    dy <- array(NA, dim=c(2, 3))
    dy[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq16]
    dy[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ][, errplaq16]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq16]^2)
    dy[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ][, errplaq16]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq16]^2)
    if(meanormedian=="mean") {
      plotwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$betacontlim, 
                    y=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$plaq16contlim, 
                    dx=dx, dy=dy, errsum.method = "quadrature", rep=T, col=cols[index], pch=pchs[index], ...)
      newline$P16 <- ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$plaq16contlim
      newline[, c("P16stat", "P16sys", "P16spread")] <- dy
    } else {
      mdx <- array(NA, dim=c(2, 3))
      mdx[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta 
      mdx[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ]$q16beta^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta^2)
      mdx[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$q16beta^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta^2)
      mdy <- array(NA, dim=c(2, 3))
      mdy[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq16
      mdy[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ]$q16plaq16^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq16^2)
      mdy[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$q16plaq16^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq16^2)
      
      plotwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianbeta, 
                    y=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianplaq16, 
                    dx=dx, dy=dy, mdy=mdy, mdx=mdx, errsum.method = "quadrature", rep=T, col=cols[index], pch=pchs[index], ...)
      
      newline$P16 <- ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianplaq3
      newline[, c("P16statq16", "P16sysq16", "P16spreadq16")] <- dy
      newline[, c("P16statq84", "P16sysq84", "P16spreadq84")] <- mdy
    }
    conf <- c()
    for(devstd in c(as.numeric(resellipse[maskresellipse & resellipse$mode==mode & resellipse$etp==1 & resellipse$betaiso==1.7 & resellipse$spread==T, ]$devstd), 
                    as.numeric(resellipse[maskresellipse & resellipse$mode==mode & resellipse$etp==1 & resellipse$betaiso==1.65 & resellipse$spread==T, ]$devstd))) {
      root <- uniroot(fninterval, interval=c(0, 10), devstd=devstd)
      conf <- append(conf, root$root)
    }
    shortres <- rbind(shortres, data.frame(betamatch1.7=tex.catwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.7 & ldata$spread==T, ]$betacontlim, 
                                                                         dx=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.7 & ldata$spread==T, ]$dbetacontlim,
                                                                         digits=2, with.dollar = F, with.cdot = F), 
                                           dev1.7=conf[1],
                                           rad1.7=as.numeric(resellipse[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.7 & ldata$spread==T, ]$devstd),
                                           betamatch1.65=tex.catwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.65 & ldata$spread==T, ]$betacontlim, 
                                                                          dx=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.65 & ldata$spread==T, ]$dbetacontlim,
                                                                          digits=2, with.dollar = F, with.cdot = F),
                                           dev1.65=conf[2], 
                                           rad1.65=as.numeric(resellipse[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.65 & ldata$spread==T, ]$devstd)))
    newline$dev=conf
    newline$rad=as.numeric(resellipse[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$devstd)
    longres <- rbind(longres, newline)
  }
  
  plotwitherror(x=hamiltoniandata$lowerx, y=hamiltoniandata$lower, col="black", type="o", pch=24, bg="black", rep=T)
  legend(x="bottomright", legend=c("H", modes), col=c("black", cols), pch=c(24, pchs), ncol=2, pt.bg=c("black", cols))
  rownames(shortres) <- modes
  # shortres[, c("dev1.7", "dev1.65")] <- shortres[, c("dev1.7", "dev1.65")] / sqrt(2.28)
  knitr::kable(shortres)
  # print(dx)
  return(longres)
}
```


```{r summaryratio}
summarisedataratio <- function(ldata, errtype, xiinter, listellipse=listellipsemean, meanormedian="mean", resellipse=resellipsemean, plotellipse=T, ...) {
  stopifnot(meanormedian=="mean" || meanormedian=="median")
  if(meanormedian=="mean") {
    errbeta <- "dbetacontlim"
    errplaq16 <- "dplaq16contlim"
    errplaq3 <- "dplaq3ratiocontlim"
    longres <- data.frame(beta=c(), mode=c(), betamatch=c(), dev=c(), rad=c(), 
                          betamatchstat=c(), betamatchsys=c(), betamatchspread=c(), 
                          P3=c(), P3stat=c(), P3sys=c(), P3spread=c(), 
                          P16=c(), P16stat=c(), P16sys=c(), P16spread=c())
  } else {
    errbeta <- "q84beta"
    errplaq16 <- "q84plaq16"
    errplaq3 <- "q84plaq3ratio"
    longres <- data.frame(beta=c(), mode=c(), betamatch=c(), dev=c(), rad=c(), 
                          betamatchstatq16=c(), betamatchsysq16=c(), betamatchspreadq16=c(), betamatchstatq84=c(), betamatchsysq84=c(), betamatchspreadq84=c(), 
                          P3=c(), P3statq16=c(), P3sysq16=c(), P3spreadq16=c(), P3statq84=c(), P3sysq84=c(), P3spreadq84=c(), 
                          P16=c(), P16statq16=c(), P16sysq16=c(), P16spreadq16=c(), P16statq84=c(), P16sysq84=c(), P16spreadq84=c())
  }
  mask <- ldata$errtype==errtype & ldata$xiinter==xiinter
  
  plot(NA, xlab="beta", ylab="P", ylim=c(0.60, 0.67), xlim=c(1.35, 1.49), ...)
  # plot(NA, xlab="beta", ylab="P", ylim=c(0, 2), xlim=c(0, 2), ...)
  modes <- c("xi0.18", "xi0.19", "xi0.20", "xi0.18wo0.19")
  cols <- c("red", "blue", "darkgreen", "magenta")
  pchs <- c(21, 22, 23)
  shortres <- data.frame(betamatch1.65=c(), dev1.65=c(), rad1.65=c(), betamatch1.7=c(), dev1.7=c(), rad1.7=c())
  
  for(index in seq_along(modes)) {
    mode=modes[index]
    # print(ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ])
    dx <- array(NA, dim=c(2, 3))
    dx[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errbeta]
    dx[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ][, errbeta]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errbeta]^2)
    dx[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ][, errbeta]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errbeta]^2)
    dy <- array(NA, dim=c(2, 3))
    dy[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq3]
    dy[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ][, errplaq3]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq3]^2)
    dy[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ][, errplaq3]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq3]^2)
    if(meanormedian=="mean") {
      plotwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$betacontlim, 
                    y=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$plaq3ratiocontlim, 
                    dx=dx, dy=dy, errsum.method = "quadrature", rep=T, col=cols[index], bg=cols[index], pch=pchs[index], ...)
      
      # print(which(resellipse$errtype==errtype & resellipse$xiinter==xiinter & resellipse$mode==mode & resellipse$etp==1 & resellipse$spread==T))
      # lapply(listellipse[which(resellipse$errtype==errtype & resellipse$xiinter==xiinter & resellipse$mode==mode & resellipse$etp==1 & resellipse$spread==T)],
      #        FUN = function(x) print(data.frame(meanx = x$medianbeta, meany = x$medianplaq3,
      #                                           radx = x$q16beta, rady = x$q84plaq3,
      #                                           phi = x$theta, nstd = as.numeric(x$devstd))))
      if(plotellipse) {
        plotlims <- lapply(listellipse[which(resellipse$errtype==errtype & resellipse$xiinter==xiinter & resellipse$mode==mode & resellipse$etp==1 & resellipse$spread==T)], 
                           FUN = function(x) draw_ellipse_general(meanx = x$betacontlim, meany = x$plaq3ratiocontlim, 
                                                                  radx = x$dbetacontlim, rady = x$dplaq3ratiocontlim, 
                                                                  phi = x$theta, nstd = as.numeric(x$devstd), 
                                                                  rep = T, cex = 0.01, points = 5000, col=cols[index]))
      }
      
      newline <- data.frame(beta=c(1.65, 1.7), mode=mode, betamatch=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$betacontlim, dev=NA, rad=NA, 
                            betamatchstat=dx[, 1], betamatchsys=dx[, 2], betamatchspread=dx[, 3],
                            P3=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$plaq3ratiocontlim, 
                            P3stat=dy[, 1], P3sys=dy[, 2], P3spread=dy[, 3])
    } else {
      mdx <- array(NA, dim=c(2, 3))
      mdx[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta 
      mdx[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ]$q16beta^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta^2)
      mdx[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$q16beta^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta^2)
      mdy <- array(NA, dim=c(2, 3))
      mdy[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq3ratio 
      mdy[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ]$q16plaq3^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq3^2)
      mdy[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$q16plaq3^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq3^2)
      plotwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianbeta, 
                    y=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianplaq3ratio, 
                    dx=dx, dy=dy, mdy=mdy, mdx=mdx, errsum.method = "quadrature", rep=T, col=cols[index], bg=cols[index], pch=pchs[index], ...)
      if(plotellipse) {
        plotlims <- lapply(listellipse[which(resellipse$errtype==errtype & resellipse$xiinter==xiinter & resellipse$mode==mode & resellipse$etp==1 & resellipse$spread==T)], 
                           FUN = function(x) draw_ellipse_general(meanx = x$medianbeta, meany = x$medianplaq3ratio, 
                                                                  radx = x$q16beta, rady = x$q84plaq3ratio, 
                                                                  phi = x$theta, nstd = as.numeric(x$devstd), 
                                                                  rep = T, cex = 0.01, points = 5000, col=cols[index]))
      }
      
      newline <- data.frame(beta=c(1.65, 1.7), mode=mode, betamatch=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianbeta, dev=NA, rad=NA, 
                            betamatchstatq16=dx[, 1], betamatchsysq16=dx[, 2], betamatchspreadq16=dx[, 3], betamatchstatq84=mdx[, 1], betamatchsysq84=mdx[, 2], betamatchspreadq84=mdx[, 3],
                            P3=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianplaq3ratio, 
                            P3statq16=dy[, 1], P3sysq16=dy[, 2], P3spreadq16=dy[, 3], P3statq84=mdy[, 1], P3sysq84=mdy[, 2], P3spreadq84=mdy[, 3])
    }
    
    
    dy <- array(NA, dim=c(2, 3))
    dy[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq16]
    dy[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ][, errplaq16]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq16]^2)
    dy[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ][, errplaq16]^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ][, errplaq16]^2)
    if(meanormedian=="mean") {
      plotwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$betacontlim, 
                    y=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$plaq16contlim, 
                    dx=dx, dy=dy, errsum.method = "quadrature", rep=T, col=cols[index], pch=pchs[index], ...)
      newline$P16 <- ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$plaq16contlim
      newline[, c("P16stat", "P16sys", "P16spread")] <- dy
    } else {
      mdx <- array(NA, dim=c(2, 3))
      mdx[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta 
      mdx[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ]$q16beta^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta^2)
      mdx[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$q16beta^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16beta^2)
      mdy <- array(NA, dim=c(2, 3))
      mdy[, 1] <- ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq16
      mdy[, 2] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==F, ]$q16plaq16^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq16^2)
      mdy[, 3] <- sqrt(ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$q16plaq16^2 - ldata[mask & ldata$mode==mode & ldata$etp==0 & ldata$spread==F, ]$q16plaq16^2)
      
      plotwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianbeta, 
                    y=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianplaq16, 
                    dx=dx, dy=dy, mdy=mdy, mdx=mdx, errsum.method = "quadrature", rep=T, col=cols[index], pch=pchs[index], ...)
      
      newline$P16 <- ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$medianplaq16
      newline[, c("P16statq16", "P16sysq16", "P16spreadq16")] <- dy
      newline[, c("P16statq84", "P16sysq84", "P16spreadq84")] <- mdy
    }
    conf <- c()
    for(devstd in c(as.numeric(resellipse[resellipse$errtype==errtype & resellipse$xiinter==xiinter & resellipse$mode==mode & resellipse$etp==1 & resellipse$spread==T & resellipse$betaiso==1.65, ]$devstd), 
                    as.numeric(resellipse[resellipse$errtype==errtype & resellipse$xiinter==xiinter & resellipse$mode==mode & resellipse$etp==1 & resellipse$spread==T & resellipse$betaiso==1.70, ]$devstd))) {
      root <- uniroot(fninterval, interval=c(0, 10), devstd=devstd)
      conf <- append(conf, root$root)
    }
    shortres <- rbind(shortres, data.frame(betamatch1.7=tex.catwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.7 & ldata$spread==T, ]$betacontlim, 
                                                                         dx=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.7 & ldata$spread==T, ]$dbetacontlim,
                                                                         digits=2, with.dollar = F, with.cdot = F), 
                                           dev1.7=conf[1],
                                           rad1.7=as.numeric(resellipse[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.7 & ldata$spread==T, ]$devstd),
                                           betamatch1.65=tex.catwitherror(x=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.65 & ldata$spread==T, ]$betacontlim, 
                                                                          dx=ldata[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.65 & ldata$spread==T, ]$dbetacontlim,
                                                                          digits=2, with.dollar = F, with.cdot = F),
                                           dev1.65=conf[2], 
                                           rad1.65=as.numeric(resellipse[mask & ldata$mode==mode & ldata$etp==1 & ldata$betaiso==1.65 & ldata$spread==T, ]$devstd)))
    newline$dev=conf
    newline$rad=as.numeric(resellipse[mask & ldata$mode==mode & ldata$etp==1 & ldata$spread==T, ]$devstd)
    longres <- rbind(longres, newline)
  }
  
  plotwitherror(x=hamiltoniandata$lowerx, y=hamiltoniandata$lower, col="black", type="o", pch=24, bg="black", rep=T)
  legend(x="bottomright", legend=c("H", modes), col=c("black", cols), pch=c(24, pchs), ncol=2, pt.bg=c("black", cols))
  rownames(shortres) <- modes
  # shortres[, c("dev1.7", "dev1.65")] <- shortres[, c("dev1.7", "dev1.65")] / sqrt(2.28)
  knitr::kable(shortres)
  # print(dx)
  return(longres)
}

# hamresults: a, b, lowerx, upperx
interpolatehamiltonian <- function(x, hamresults) {
  rightsegment <- x > hamresults$lowerx & x < hamresults$upperx
  return(hamresults$a[rightsegment] * x + hamresults$b[rightsegment])
}
```


We first check if the mean is a reliable quantity by plotting the mean $\pm$ standard deviation against the median with the 16% and 84% quantiles.

```{r meanvsmedian}

for(beta in c(1.65, 1.7)) {
  plotwitherror(x=seq_along(ldata$betacontlim[ldata$betaiso==beta]), y=ldata$betacontlim[ldata$betaiso==beta], dy=ldata$dbetacontlim[ldata$betaiso==beta], col="black", pch=21, bg="black", 
                ylim=range(ldata$betacontlim[ldata$betaiso==beta] + ldata$dbetacontlim[ldata$betaiso==beta], 
                           ldata$betacontlim[ldata$betaiso==beta] - ldata$dbetacontlim[ldata$betaiso==beta], 
                           ldata$medianbeta[ldata$betaiso==beta]), 
                xlab="index", ylab="beta", xlim=range(seq_along(ldata$betacontlim[ldata$betaiso==beta])), main=paste("beta", beta, "cont limit beta"))
  plotwitherror(x=seq_along(ldata$betacontlim[ldata$betaiso==beta])+0.2, y=ldata$medianbeta[ldata$betaiso==beta], dy=ldata$q84beta[ldata$betaiso==beta], mdy=ldata$q16beta[ldata$betaiso==beta], col="red", pch=22, bg="red", rep=T)
  abline(v=length(seq_along(ldata$betacontlim[ldata$betaiso==beta]))*c(1/3, 2/3)+0.5)
  legend(x="bottomleft", legend="AIC", bty = "n")
  legend(x="bottom", legend="error", bty = "n")
  legend(x="bottomright", legend="unweighted", bty = "n")
  
  plotwitherror(x=seq_along(ldata$betacontlim[ldata$betaiso==beta]), y=ldata$plaq3contlim[ldata$betaiso==beta], dy=ldata$dplaq3contlim[ldata$betaiso==beta], col="black", pch=21, bg="black", 
                ylim=range(ldata$plaq3contlim[ldata$betaiso==beta] + ldata$dplaq3contlim[ldata$betaiso==beta], 
                           ldata$plaq3contlim[ldata$betaiso==beta] - ldata$dplaq3contlim[ldata$betaiso==beta], 
                           ldata$medianplaq3[ldata$betaiso==beta]), 
                xlab="index", ylab="plaq3", xlim=range(seq_along(ldata$betacontlim[ldata$betaiso==beta])), main=paste("beta", beta, "cont limit plaq3"))
  plotwitherror(x=seq_along(ldata$betacontlim[ldata$betaiso==beta])+0.2, y=ldata$medianplaq3[ldata$betaiso==beta], dy=ldata$q84plaq3[ldata$betaiso==beta], mdy=ldata$q16plaq3[ldata$betaiso==beta], col="red", pch=22, bg="red", rep=T)
  abline(v=length(seq_along(ldata$betacontlim[ldata$betaiso==beta]))*c(1/3, 2/3)+0.5)
  legend(x="bottomleft", legend="AIC", bty = "n")
  legend(x="bottom", legend="error", bty = "n")
  legend(x="bottomright", legend="unweighted", bty = "n")
}
```


We see that the standard deviation is not reliable in some cases, so we take the unweighted average over all different continuum limit fits to be the final result.

we use the xi that was determined from the single matching ensembles, and we do not consider the spread of the different fits of the continuum limit as an additional systematic error.

We can display the results, matching beta and deviations from the Hamiltonian result for these choices.
The data at L=3 are shown by filled symbols, the data at L=16 by empty symbols.


```{r makesummaries}
errtype="unweighted"

tablemean             <- summarisedata(ldata=ldata, errtype=errtype, xiinter=T, listellipse = listellipsemean,        resellipse=resellipsemean,        meanormedian="mean", plotellipse=T, main="mean")
tablemedian           <- summarisedata(ldata=ldata, errtype=errtype, xiinter=T, listellipse = listellipsemedian,      resellipse=resellipsemedian,      meanormedian="median", plotellipse=T, main="median")
tablemeanratio   <- summarisedataratio(ldata=ldata, errtype=errtype, xiinter=T, listellipse = listellipsemeanratio,   resellipse=resellipsemeanratio,   meanormedian="mean", plotellipse=T, main="mean ratio")
tablemedianratio <- summarisedataratio(ldata=ldata, errtype=errtype, xiinter=T, listellipse = listellipsemedianratio, resellipse=resellipsemedianratio, meanormedian="median", plotellipse=T, main="median ratio")
silent <-      summarisedata(ldata=ldata, errtype=errtype, xiinter=T, listellipse = listellipsemean, resellipse=resellipsemean, meanormedian="mean", plotellipse=F, main="mean")
silent <-      summarisedata(ldata=ldata, errtype=errtype, xiinter=T, listellipse = listellipsemedian, resellipse=resellipsemedian, meanormedian="median", plotellipse=F, main="median")
silent <- summarisedataratio(ldata=ldata, errtype=errtype, xiinter=T, listellipse = listellipsemeanratio, resellipse=resellipsemeanratio, meanormedian="mean", plotellipse=F, main="mean ratio")
silent <- summarisedataratio(ldata=ldata, errtype=errtype, xiinter=T, listellipse = listellipsemedianratio, resellipse=resellipsemedianratio, meanormedian="median", plotellipse=F, main="median ratio")
```


```{r comparesummaries}
tablemean$P3 - tablemeanratio$P3
sqrt(tablemean$P3stat^2 + tablemeanratio$P3stat^2)
plotwitherror(x=1:8, 
y=tablemean$P3 - tablemeanratio$P3,
dy=sqrt(tablemean$P3stat^2 + tablemeanratio$P3stat^2))
abline(h=0)
# plotwitherror(x=1:8, 
# y=tablemedian$P3 - tablemedianratio$P3,
# dy=sqrt(tablemedian$P3stat^2 + tablemedianratio$P3stat^2))
# abline(h=0)
tablemean
plot(x=1:32, y=c(tablemean$P3spread^2+tablemean$P3sys^2 + tablemean$P3stat^2, 
                 tablemedian$P3spreadq84^2+tablemedian$P3sysq84^2 + tablemedian$P3statq84^2, 
                 tablemeanratio$P3spread^2+tablemeanratio$P3sys^2 + tablemeanratio$P3stat^2,
                 tablemedianratio$P3spreadq84^2+tablemedianratio$P3sysq84^2 + tablemedianratio$P3statq84^2))
```

The error of the matching $\beta$ is in the order of $1\%$, the deviation to the Hamiltonian curve is in the order of $3\%$. 
The level of deviation for the median is calculated with the difference between median and the 84%-percent for the plaquette (upper value) and the difference to the 16%-quantile for beta (left value).
The median beta is higher than the mean beta, this leads to an increase in the level of deviation.
The level of deviation now includes the conversion factor from the 1D one-sigma interval to the 2D one-sigma interval, and is chosen such that $68%$ of points are within the ellipse with deviation one sigma.